\LARGE \bf Generalizing Informed Sampling for Asymptotically Optimal Sampling-based Planning via Markov Chain Monte Carlo Methods

### 2017-09-13 paper.tex

\title{\LARGE \bf
Informed sampling by Markov Chain Monte Carlo methods
}

@@

\subsection{Motivating example---Minimal-Time Double Integrator (MTDI)}
\label{sec:mtdi}

@@

@@

@@

@@

\section{Conclusion}

>>>>

\title{\LARGE \bf
Generalizing Informed Sampling
for Asymptotically Optimal Sampling-based Planning via Markov Chain
Monte Carlo Methods
}

@@

\subsection{Motivating example---Minimal-Time Double Integrator}
\label{sec:mtdi}

\os{mention~\cite{LM97} here or in related work}

@@

\os{mention that it is AO}

@@

\os{Mention that we do not need convexity}

@@

\os{Explain why MCMC is flat, mention strawman approach}

@@

\section{Conclusion}
\os{Discuss param tuning, we did nothing + there is a wealth of literature}

\os{use with BIT*, challenge - distance function is not a metric}
